---
title: "Stawberry3"
output: pdf_document
author: Ziheng Li
date: "2024-10-31"
---

```{r}

library(magrittr)
library(dplyr)
library(stringr)
library(readr)
library(ggplot2)
library(tidyverse)
library(PubChemR)

```

```{r}
strawberry_chem <- read_csv("survey_d_chem.csv",show_col_types = FALSE)
chemical_type <- strawberry_chem$type
head(chemical_type)
```
```{r}

california_data <- filter(strawberry_chem, State == "CALIFORNIA")
unique_types <- unique(california_data$type)
print(unique_types)

```

```{r}
strawberry_chem$Value <- as.numeric(as.character(strawberry_chem$Value))

# Define a function to filter data by type, compute mean values, and plot top 20 chemicals
plot_top_20_chemicals <- function(type_name) {
  # Filter data by type and calculate mean values
  type_data <- strawberry_chem %>%
    filter(type == type_name) %>%
    group_by(chem_name) %>%
    summarise(mean_value = mean(Value, na.rm = TRUE), .groups = 'drop') %>%
    arrange(desc(mean_value)) %>%
    slice_head(n = 20)
  
  # Plotting the top 20 chemicals
  plot <- ggplot(type_data, aes(x = reorder(chem_name, -mean_value), y = mean_value, fill = chem_name)) +
    geom_col() +
    coord_flip() +  # Flips the axes for better label readability
    labs(x = "Chemical Name", y = "Average Value", title = paste("Top 20 Average Values in", type_name)) +
    theme_minimal() +
    theme(axis.text.y = element_text(size = 5))  # Adjust text size for readability
  
  print(plot)
}

# Apply the function to each type
plot_top_20_chemicals("FUNGICIDE")
```
Fungicides: The chart shows a range of chemicals for which the mean values for phenyl ether metronidazole and tetraconazole are significantly higher, indicating higher utilization, efficacy or cost.

```{r}
plot_top_20_chemicals("INSECTICIDE")
```
Insecticides: Azadirachtin and Spinetoram lead in average values, suggesting their major roles in insect control. Azadirachtin, derived from neem trees, also suggests a preference for bio-based insecticides.The wide range of chemicals indicates a variety of approaches to pest management, reflecting different application requirements and target species.
```{r}
plot_top_20_chemicals("OTHER")
```

Other: The high average values of these chemicals could reflect their crucial role in preparing fields for planting by controlling soil-borne pests and diseases.
```{r}
plot_top_20_chemicals("HERBICIDE")
```
Herbicides: The dominance of Oxyfluorfen and Paraquat in average values points to their widespread use, possibly due to their effectiveness in controlling a broad range of weeds.The presence of several different active ingredients suggests a strategic approach to herbicide resistance management.

```{r}
GHS_searcher<-function(result_json_object){
  result<-result_json_object
  for (i in 1:length(result[["result"]][["Hierarchies"]][["Hierarchy"]])){
    if(result[["result"]][["Hierarchies"]][["Hierarchy"]][[i]][["SourceName"]]=="GHS Classification (UNECE)"){
      return(i)
    }
          
  }
}
```

```{r}
hazards_retriever<-function(index,result_json_object){
  result<-result_json_object
  hierarchy<-result[["result"]][["Hierarchies"]][["Hierarchy"]][[index]]
  i<-1
  output_list<-rep(NA,length(hierarchy[["Node"]]))
  while(str_detect(hierarchy[["Node"]][[i]][["Information"]][["Name"]],"H") & i<length(hierarchy[["Node"]])){
    output_list[i]<-hierarchy[["Node"]][[i]][["Information"]][["Name"]]
    i<-i+1
  }
  return(output_list[!is.na(output_list)])
}
```

```{r}
chemical_vec<-c("azoxystrobin","flumioxazin")

result_f<-get_pug_rest(identifier = "flumioxazin", namespace = "name", domain = "compound",operation="classification", output = "JSON")

hazards_retriever(GHS_searcher(result_f),result_f)


result_d<-get_pug_rest(identifier = "hexythiazox", namespace = "name", domain = "compound",operation="classification", output = "JSON")

hazards_retriever(GHS_searcher(result_d),result_d)
```
